On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-04-06 manuscripts/PNAS/chazthm_pnas.tex
changes
eqn ref

\section{Results}

@@

%In other words, the smaller the difference $\bar m - m$, the more columns and coefficients of the original $n \times m$ dictionary $\mathbf{A}$ and $m$-dimensional codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \bar m$ dictionary $\mathbf{B}$ and $\bar m$-dimensional codes $\mathbf{\bar x}_i$. In particular, when $\bar m = m$ all columns of $\mathbf{A}$ and coefficients of each $\mathbf{x}_i$ recoverable, as per Def.~\ref{maindef}.

@@

Fix $F \subseteq E$. Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \textbf{0}$ then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as $\mathbf{B}_i \neq \textbf{0}$ for all $i$) and \eqref{cond} trivially holds. Suppose then that the intersection is not the zero vector. By Lem.~\ref{SpanIntersectionLemma} and Lem.~\ref{DistanceToIntersectionLemma}, and incorporating \eqref{eq2} and \eqref{GapUpperBound}, we have:
\begin{align}\label{randoml}
d( \text{\rm Span}&\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}, \text{\rm Span}\{\mathbf{A}_{\cap_{S \in F} S}\}  ) \nonumber \\
&\leq d\left( \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}, \cap_{S \in F} \text{\rm Span}\{\mathbf{A}_{S}\} \right) \nonumber \\
&\leq \sum_{S \in F} \frac{ d\left( \cap_{T \in F} \text{\rm Span}\{\mathbf{B}_{\pi(T)}\},\text{\rm Span}\{\mathbf{A}_{S}\} \right) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{T}\}_{T \in F}) } \nonumber \\
&\leq \sum_{S \in F} \frac{ d\left( \text{\rm Span}\{\mathbf{B}_{\pi(S)}\},\text{\rm Span}\{\mathbf{A}_{S}\} \right) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{T}\}_{T \in F}) }\nonumber \\
%&\leq \frac{1}{r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F})} \sum_{S \in F} \frac{ \varepsilon }{ L(\mathbf{AX}_{J(S)}) } \nonumber \\
&\leq \frac{|F| \varepsilon}{r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})} 
%&< L_2(\mathbf{A}) \frac{|F| }{ 2^{|E|}} \left( \frac{ \min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) } \right) \left( \frac{\min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }{ \min_{T \in F} L(\mathbf{AX}_{J(T)}) } \right) \nonumber \\
\leq C_2 \varepsilon. 
\end{align}
Note that since $\varepsilon < L_2(\mathbf{A}) / \tilde C_2$, by \eqref{delrho} the right-hand side in \eqref{randoml} is strictly less than one, so \eqref{dimLem} implies that $\dim(\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}) \leq \dim(\text{\rm Span}\{\mathbf{A}_{\cap_{S \in F} S}\})$ and \eqref{fact2} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
Now, fix $\ell \in [m]$. Since $E$ satisfies the singleton intersection property, $\{\ell\} = \cap F(\ell)$ for the star $F(\ell) \subseteq E$. By \eqref{cond}, we have that $\cap_{S \in F(\ell)} \pi(S)$ is either empty or it contains a single element. Lem.~\ref{NonEmptyLemma} ensures the latter case is the only possibility. Thus, the association $\ell \mapsto \cap_{S \in F(\ell)} \pi(S)$ defines a map $\bar \pi: [m] \to [m]$ and $\dim(\text{\rm Span}\{\mathbf{B}_{\bar \pi(\ell)}\}) = 1$, since $\mathbf{B}_i \neq \textbf{0}$ for all $i$. By \eqref{eqdim}, it follows from \eqref{randoml} that $d\left( \text{\rm Span}\{\mathbf{A}_\ell\}, \text{\rm Span}\{ \mathbf{B}_{\bar \pi(\ell)} \} \right) \leq C_2 \varepsilon$. Since $\ell$ is arbitrary, fixing $\bar \varepsilon = C_2\delta$ it follows from \eqref{randoml} that for every basis vector $\mathbf{e}_\ell \in \mathbb{R}^m$ there exists some $c'_\ell \in \mathbb{R}$ such that $\|\mathbf{A}\mathbf{e}_\ell - c'_\ell \mathbf{B}\mathbf{e}_{\bar \pi(\ell)}\|_2 \leq \bar \varepsilon < L_2(\mathbf{A})$. This is exactly the supposition in \eqref{1D} (letting $c_i = \|\mathbf{A}_i\|_2^{-1}$ for all $i$) and the result follows from the subsequent arguments for the case $k=1$ in Sec.~\ref{DUT}.
\end{proof}

>>>>

\section{Results}\label{Results}

@@

%In other words, the smaller the difference $\bar m - m$, the more columns and coefficients of the original $n \times m$ dictionary $\mathbf{A}$ and $m$-dimensional codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \bar m$ dictionary $\mathbf{B}$ and $\bar m$-dimensional codes $\mathbf{\bar x}_i$. 
%In particular, when $\bar m = m$ all columns of $\mathbf{A}$ and coefficients of each $\mathbf{x}_i$ recoverable, as per Def.~\ref{maindef}.

@@

Fix $F \subseteq E$. Since $\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\} \subseteq \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}$, if $\cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\} = \textbf{0}$ then we must have $|\cap_{S \in F} \pi(S)| = 0$ (as $\mathbf{B}_i \neq \textbf{0}$ for all $i$) and \eqref{cond} trivially holds. Suppose then that the intersection is not the zero vector. By Lem.~\ref{SpanIntersectionLemma} and Lem.~\ref{DistanceToIntersectionLemma}, and incorporating \eqref{eq2} and \eqref{GapUpperBound}, we have:
\begin{align}\label{randoml}
d( \text{\rm Span}&\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}, \text{\rm Span}\{\mathbf{A}_{\cap_{S \in F} S}\}  ) \nonumber \\
&\leq d\left( \cap_{S \in F} \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}, \cap_{S \in F} \text{\rm Span}\{\mathbf{A}_{S}\} \right) \nonumber \\
&\leq \sum_{S \in F} \frac{ d\left( \cap_{T \in F} \text{\rm Span}\{\mathbf{B}_{\pi(T)}\},\text{\rm Span}\{\mathbf{A}_{S}\} \right) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{T}\}_{T \in F}) } \nonumber \\
&\leq \sum_{S \in F} \frac{ d\left( \text{\rm Span}\{\mathbf{B}_{\pi(S)}\},\text{\rm Span}\{\mathbf{A}_{S}\} \right) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{T}\}_{T \in F}) }\nonumber \\
%&\leq \frac{1}{r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F})} \sum_{S \in F} \frac{ \varepsilon }{ L(\mathbf{AX}_{J(S)}) } \nonumber \\
&\leq \frac{|F| \varepsilon}{r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F})} 
%&< L_2(\mathbf{A}) \frac{|F| }{ 2^{|E|}} \left( \frac{ \min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) }{ r( \{ \text{\rm Span}\{\mathbf{A}_{S}\}_{S \in F}) } \right) \left( \frac{\min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }{ \min_{T \in F} L(\mathbf{AX}_{J(T)}) } \right) \nonumber \\
\leq C_2 \varepsilon. 
\end{align}
Note that since $\varepsilon < L_2(\mathbf{A}) / \tilde C_2$, by \eqref{delrho} the right-hand side in \eqref{randoml} is strictly less than one, so \eqref{dimLem} implies that $\dim(\text{\rm Span}\{\mathbf{B}_{\cap_{S \in F}\pi(S)}\}) \leq \dim(\text{\rm Span}\{\mathbf{A}_{\cap_{S \in F} S}\})$ and \eqref{cond} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in F$.
Now, fix $\ell \in [m]$. Since $E$ satisfies the singleton intersection property, $\{\ell\} = \cap F(\ell)$ for the star $F(\ell) \subseteq E$. By \eqref{cond}, we have that $\cap_{S \in F(\ell)} \pi(S)$ is either empty or it contains a single element. Lem.~\ref{NonEmptyLemma} ensures the latter case is the only possibility. Thus, the association $\ell \mapsto \cap_{S \in F(\ell)} \pi(S)$ defines a map $\bar \pi: [m] \to [m]$ and $\dim(\text{\rm Span}\{\mathbf{B}_{\bar \pi(\ell)}\}) = 1$, since $\mathbf{B}_i \neq \textbf{0}$ for all $i$. By \eqref{eqdim}, it follows from \eqref{randoml} that $d\left( \text{\rm Span}\{\mathbf{A}_\ell\}, \text{\rm Span}\{ \mathbf{B}_{\bar \pi(\ell)} \} \right) \leq C_2 \varepsilon$. Since $\ell$ is arbitrary, fixing $\bar \varepsilon = C_2\delta$ it follows from \eqref{randoml} that for every basis vector $\mathbf{e}_\ell \in \mathbb{R}^m$ there exists some $c'_\ell \in \mathbb{R}$ such that $\|\mathbf{A}\mathbf{e}_\ell - c'_\ell \mathbf{B}\mathbf{e}_{\bar \pi(\ell)}\|_2 \leq \bar \varepsilon < L_2(\mathbf{A})$. This is exactly the supposition in \eqref{1D} (letting $c_i = \|\mathbf{A}_i\|_2^{-1}$ for all $i$) and the result follows from the subsequent arguments for the case $k=1$ in Sec.~\ref{DUT}.
\end{proof}
